---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rivertopo

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/WeiquanLuo/rivertopo.svg?branch=master)](https://travis-ci.org/WeiquanLuo/rivertopo)
<!-- badges: end -->

The goal of rivertopo is to simplify a given tree topology (ie. for River network) with given locations. For example:

* convert object class `rivernetwork` from riverdist package to river topology in form of arcs between vertice.

```{r}
# resulted river topology
data.frame(from = c("Vertex1", "Vertex2"), to = c("Vertex2", "Vertex3"))
```

* convert a list of interesting location points into topological structure by mapping it on a given river topology  


```{r}
# given location point:
data.frame(id = c("Point1", "Point2", "Point3"),
                   lat = c(42.032974, 44.032323, 47.123123),
                   long = c(-93.581543, -92.58345343, -96.2324543),
                   stringsAsFactors = FALSE)

# resulted location topology:
data.frame(from = c("Point1", "Point2"), to = c("Point2", "Point3"))
```


## Installation

You can install the released version of rivertopo from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("WeiquanLuo/rivertopo")
# install.packages("rivertopo") # not yet avaliable
```

## Example

Not yet avaliable
